---
title: "FIFA Data Analysis"
author: "Konner Macias"
date: "February 1, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Data and 
```{r}
df <- read.csv('Data/FifaTrainNew.csv', stringsAsFactors = F)
```

Understand structure
```{r}
str(df)
```

```{r}
head(df)
```


```{r}
library(ggplot2)
ggplot(df, aes(WageNew, fill = WageNew)) + geom_density(position = "stack")
```

I'd like to look at the top wage values
```{r}
plot(sort(df$WageNew, decreasing = T)[1:250])
plot(sort(df$WageNew, decreasing = T)[250:1000])
```



We will look for any correlation with the variables
```{r}
#install.packages("corrplot")
library(corrplot)
# select only numeric columns
num_inds <- unlist(lapply(df, is.numeric))
cor_matrix <- cor(df[num_inds])
cor_matrix
```

Clean up club names.
```{r}
for (i in 1:length(df$Club))
{
  if (is.na(df$Club[i])) { next }
  # replace with appropriate characters
  club <- df$Club[i]
  if (grepl('<e9>', club)) { df$Club[i] <- gsub("<e9>","é", club) }
  else if (grepl('<f3>', club)) { df$Club[i] <- gsub("<f3>","o", club) }
  else if (grepl('<f8>', club)) { df$Club[i] <- gsub("<f8>","o", club) }
  else if (grepl('<d6>', club)) { df$Club[i] <- gsub("<d6>","o", club) }
  else if (grepl('<e6>', club)) { df$Club[i] <- gsub("<e6>","a", club) }
  else if (grepl('<e3>', club)) { df$Club[i] <- gsub("<e3>","a", club) }
  else if (grepl('<e1>', club)) { df$Club[i] <- gsub("<e1>","a", club) }
  else if (grepl('<c1>', club)) { df$Club[i] <- gsub("<c1>","a", club) }
  else if (grepl('<ea>', club)) { df$Club[i] <- gsub("<ea>","ê", club) }
  else if (grepl('<ee>', club)) { df$Club[i] <- gsub("<ee>","î", club) }
  else if (grepl('<c7>', club)) { df$Club[i] <- gsub("<c7>","c", club) }
  else if (grepl('<f6>', club)) { df$Club[i] <- gsub("<f6>","ö", club) }
  else if (grepl('<fc>', club)) { df$Club[i] <- gsub("<fc>","u", club) }
}
```

Let's complete all cases for now, handle the other stuff later.
```{r}
df <- df[-18]
df.full <- df[complete.cases(df),]
num_inds <- unlist(lapply(df.full, is.numeric))
cor_matrix <- cor(df.full[num_inds])
cor_matrix
```

Give me all the correlations against wage in decreasing order
```{r}
sort(cor_matrix[2,], decreasing = TRUE)
```
We will look at those with over .2 correlation
```{r}
top_cors <- as.data.frame(sort(cor_matrix[2,], decreasing = TRUE)[1:20])
row.names(top_cors)
```

```{r}
inds <- c()
for (name in row.names(top_cors)) {
  inds <- c(which(names(df.full)==name), inds)
}
cor_fin <- cor(df.full[inds])
cor_fin
```

```{r}
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
chart.Correlation(cor_fin, histogram = T, pch = 19)
```



3 stars: Intl Rep, Vision, dribbling, curve, longShots, FKAccuracy
2 stars: Positioning, Closing, Volleys, SkillMoves, ShotPower
```{r}
top_vars <- c("International.Reputation","Vision","Dribbling","Curve","LongShots","FKAccuracy","Positioning","Closing","Volleys","Skill.Moves","ShotPower","WageNew")
inds <- c()
for (name in top_vars) {
  inds <- c(which(names(df.full)==name), inds)
}
cor_sml <- cor(df.full[inds])
```

Look at relationships
```{r}
chart.Correlation(cor_sml, histogram = T, pch = 19)
```



Now, let's build optimal model
```{r}
library(leaps)
library(car)
bm <- regsubsets(WageNew ~ ShotPower + Skill.Moves + Volleys + Positioning + FKAccuracy + LongShots + Curve + Dribbling + Vision + International.Reputation, data = df.full,
                 nbest=1, nvmax=NULL, force.in=NULL, force.out=NULL,method="exhaustive")
bm.sum <- summary(bm)
res.legend <-subsets(bm, statistic="adjr2", legend = FALSE, min.size = 3, max.size = 12, main = "Adjusted R^2")
```

Look at them
```{r}
which(bm.sum$which[8,] == TRUE)
```

```{r}
m1 <- lm(WageNew ~ ShotPower + Skill.Moves + Volleys + FKAccuracy + LongShots + Dribbling + Vision + International.Reputation, data = df.full)
summary(m1)
vif(m1)
```

Solid model.
```{r}
par(mfrow=c(2,2))
plot(m1)
```


lol ew.

We need to transform WageNew.
```{r}
plot(density(log(df.full$WageNew),bw="SJ",kern="gaussian"), type="l",main="Gaussian
kernel density estimate (After Transformation)",xlab="Wage New")
```


Better than nothing. Honestly, we should be created separate models? IDK

Try some inverse response plot
```{r}
jumbo <- lm(WageNew ~ ShotPower + Skill.Moves + Volleys + FKAccuracy + LongShots + Dribbling + Vision + International.Reputation + Curve + Positioning, data = df.full)
inverseResponsePlot(jumbo)
summary(powerTransform(jumbo))
```

```{r}
plot(density(I(df.full$WageNew)^(-0.2),bw="SJ",kern="gaussian"), type="l",main="Gaussian
kernel density estimate (After Transformation)",xlab="Wage New")
```

```{r}
bm.lam <- regsubsets(I(WageNew)^(-0.2) ~ ShotPower + Skill.Moves + Volleys + Positioning + FKAccuracy + LongShots + Curve + Dribbling + Vision + International.Reputation, data = df.full,
                 nbest=1, nvmax=NULL, force.in=NULL, force.out=NULL,method="exhaustive")
bm.sum <- summary(bm.lam)
res.legend <-subsets(bm, statistic="adjr2", legend = FALSE, min.size = 3, max.size = 12, main = "Adjusted R^2")
```

```{r}
which(bm.sum$which[8,] == TRUE)
```

```{r}
m2 <- lm(I(WageNew)^(-0.2) ~ ShotPower + Skill.Moves + Volleys + Curve + LongShots + Dribbling + Vision + International.Reputation, data = df.full)
summary(m2)
vif(m2)
```

```{r}
par(mfrow=c(2,2))
plot(m2)
```

A lot better.

First let's do an 80/20 split
```{r}
set.seed(76776889)
sam <- sample(nrow(df.full), nrow(df.full)*0.80)
train <- df.full[sam,]
test <- df.full[-sam,]
```

```{r}
final_variables <- c("WageNew","ShotPower", "Skill.Moves", "Volleys", "Curve", "LongShots", "Dribbling", "Vision", "International.Reputation")
inds <- c()
for (name in final_variables) {
  inds <- c(which(names(test)==name), inds)
}

testy <- test[inds]
testy$WageNewPred <- I(predict(m2, testy))^-5
row.names(testy) <- 1:nrow(testy)
```

Now see error
```{r}
sum((testy$WageNew - testy$WageNewPred)^2)/nrow(testy)
mean(abs(testy$WageNew - testy$WageNewPred))
```

```{r}
testy[testy$WageNew > 600000,]$WageNew = 600000
```




Let's make predictions
```{r}
test.df2 <- read.csv('Data/FifaTestNoYvalues.csv', stringsAsFactors = F)
test.df <- test.df2[-17]
test.df <- test.df[complete.cases(test.df),]
```

```{r}
final_variables <- c("ShotPower", "Skill.Moves", "Volleys", "Curve", "LongShots", "Dribbling", "Vision", "International.Reputation")
inds <- c()
for (name in final_variables) {
  inds <- c(which(names(test.df)==name), inds)
}

test.1 <- test.1[inds]
test.1$WageNew <- I(predict(m2, test.1))^-5
row.names(test.1) <- 1:nrow(test.1)
head(test.1)

# hack where if wage new is over 60000
```

```{r}
test.1[test.1$WageNew > 600000,]$WageNew = 600000
```

```{r}
test.1[test.1$WageNew > 590000,]
```

```{r}
my_soln <- data.frame(Ob=1:nrow(test.1), WageNew=test.1$WageNew)
write.csv(my_soln, file='pred1.csv', row.names=F)
```

